### 2018-01-21 response_to_referee.txt

     The concept of conveying an intuitive description of statistical
     methods for the broad astronomical community is certainly
     something I support, however I would like to ask the authors and
     editor to consider some caveats below.

     Novelty and references

     The draft lacks of some important literature contextualization. A
     critical one is a recent Annual Review of Astronomy and
     Astrophysics entitled Markov Chain Monte Carlo Methods for
     Bayesian Data Analysis in Astronomy
     https://arxiv.org/abs/1706.01629

Yes, we know this paper. We now cite it near the end of the first
Section, and near the beginning of Section 10. We note in both places
that the Sharma review goes into much more depth on methods than we
do; our goals here are far more introductory.

### 2018-01-21 response_to_referee.txt

     I am sure the authors are aware of the difference between both,
     and should know they don't even agree beyond simple cases: such
     as for normally distributed data. Hence the quote "Because they
     are so afraid of being confused with frequentists, Bayesians
     often call these regions "credible" rather than "confidence""

     Not only seems inappropriate for a scientific paper, but it is
     actually misleading. See for instance The fallacy of placing
     confidence in confidence intervals, Morey et al. 2015
     https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4742505/

     Moreover, such discussion -- Bayesian vs Frequentist -- has far
     deeper roots. See e.g. Probability theory, the logic of science,
     E.T. Jaynes, Cambridge University Press 2003.

Actually, our problem is with the *names*. We agree with the referee
that these two things are importantly and substantially different!
They have totally different meanings, of course. We have fixed that
all up in the text now, making it clear that these are not the same
thing at ALL. We changed both the footnote (and extended it to make
the point) and also the text that is so footnoted.

### 2018-01-21 mcmc.tex
credible issue

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are either variances or else posterior quantiles.
We usually use quantiles.
That is, the ``one-sigma'' error bar can be taken to be the half-size of the central (or smallest) interval of the parameter that contains 68 percent of the posterior
  samples.
In our own work, We usually create a 68-percent interval or region by
  excluding the top and bottom 16 percent of the
  posterior samples.  Some more aggressive investigators find the
  smallest interval that contains 68 (or 95) percent of the samples.
  Both are legitimate, and they are nearly identical for distributions
  that are nearly symmetric around the mean.
The ``two-sigma'' error bar would be the same but for the 95-percent interval
  (excluding the top and bottom 2.5 percent).
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $g(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)
  of the samples lie between them.
Again, to form these limits, $g(\pars)$ must be a scalar function (so sorting is well defined).
Because they are so afraid of being confused with frequentists,
Bayesians often call these regions ``credible'' rather than
``confidence''\note{We don't like this ``credible'' terminology,
  though we sometimes adopt it to avoid confusion.}

>>>>

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are either variances or else posterior quantiles.
We usually use quantiles.
That is, the ``one-sigma'' error bar can be taken to be the half-size of the central (or smallest) interval of the parameter that contains 68 percent of the posterior
  samples.
In our own work, We usually create a 68-percent interval or region by
  excluding the top and bottom 16 percent of the
  posterior samples.  Some more aggressive investigators find the
  smallest interval that contains 68 (or 95) percent of the samples.
  Both are legitimate, and they are nearly identical for distributions
  that are nearly symmetric around the mean.
The ``two-sigma'' error bar would be the same but for the 95-percent interval
  (excluding the top and bottom 2.5 percent).
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $g(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)
  of the samples lie between them.
Again, to form these limits, $g(\pars)$ must be a scalar function (so sorting is well defined).
Because of the danger of having them confused with frequentist uncertainties,
Bayesians usually call these regions ``credible'' rather than
``confidence'' regions.\note{We don't like this terminology, because there is
  nothing about the words ``confidence'' and ``credible'' that properly
  distinguish the difference between these very different things.
  Confidence regions say what regions of parameter space make data like the
  observed data; credible regions say what regions of parameter space are
  probable given the data. The latter require priors for their construction
  and are the intervals produced by \MCMC.}
